Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-05 ch04-lrmhinf/lrmhinf.tex
More info on AVIS/VI setup

%TODO: add section from Benchmark paper

@@

\section{Application to an \glsentryname{AVIS}}
\label{sec:lrmhinf:measurement}
The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:lrmhinf:avis}.
The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts, that is free to move in six degrees of freedom.
Six geophones measure the payload velocity and eight linear motors allow to actively compensate for vibration of the platform.
To facilitate the presentation, only the vertical translation, i.e. a \gls{SISO} system,  is considered.

@@

The parametrization of the plant model set $\ModelSet[]$ conforms to the dual-\YK{} framework~\citep{Hansen1989,Anderson1998} that parametrizes $\ModelSet[]$ in terms of  all plants $P$ that are stabilized by the controller $C$:
\begin{equation}
  \ModelSet[] 
    \isdef 
      \Set{
            \frac{\hat{N} + D_c \Delta}
                 {\hat{D} - N_c \Delta} 
          |
            \hinfnorm{\Delta} \leq \gamma
        }
  \label{eq:lrmhinf:dualYoulaModelSet}
  \text{,}
\end{equation}
where $C=N_c D_c^{-1}$ and $\estimated\Plant = \estimated{N}\estimated{D}^{-1}$ are decomposed as \gls{RCF} (see \figref{fig:lrmhinf:dualYoula}).
To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:lrmhinf:dualYoula} are required.
These can be computed from $u$ and $y$ directly~\citep{Anderson1998}:

In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:lrmhinf:LPMHinf} applies.

>>>>

@@

\section{Application to an \glsentryname{AVIS}}
\label{sec:lrmhinf:measurement}
The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:lrmhinf:avis}.
The broad aim of vibration isolation~\citep{Karnopp1995,Collette2011} is to suppress vibrations such that a certain payload (e.g. passengers in a car, sensitive equipment such as atomic force microscopes or wafer-scanners used for lithography) is not disturbed by vibrations generated by either the payload itself ($F_{\mathrm{d(pl)}}$) or by the outside world ($F_{\mathrm{d(pl)}}$) as indicated in \figref{fig:lrmhinf:vibration-isolation}.

\begin{figure}
 \centering
  \setlength{\figurewidth}{0.45\columnwidth}
  \begin{subfigure}[b]{0.49\columnwidth}
    \input{\thisDir/figs/vibrationisolation-classical.tikz}
    \caption{Traditional set-up.}  
    \label{fig:lrmhinf:vibration-isolation:traditional}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\columnwidth}
    \input{\thisDir/figs/vibrationisolation-skyhook.tikz}
    \caption{Principle of sky-hook damping.}  
    \label{fig:lrmhinf:vibration-isolation:skyhook}
  \end{subfigure}
  \disclaimer{Figure based on \citep[Fig. 3 and 4]{Voorhoeve2015SYSID} and \citep[Fig. 3 and 6]{Karnopp1995}.}
  \caption{Conceptual illustration of (active) vibration isolation set-ups. In addition to the passive isolation (spring and damper), the active controller $C$ provides additional isolation using the measurement of the payload velocity ($y=v_z$).
  If the velocity relative to ground is measured (a), the controller design involves trading-off which disturbance should be suppressed better.
  When the absolute velocity the payload is measured (b), the controller can suppress both disturbances as it acts as a damper between a virtual fixed point (``sky'') and the payload.
  }
  \label{fig:lrmhinf:vibration-isolation}
\end{figure}

The typical set-up for vibration isolation is illustrated in \figref{fig:lrmhinf:vibration-isolation:traditional}.
If the controller $C$ is removed, the set-up reduces to a passive isolation system where the suspension is to be designed such that the payload velocity $y=v_z$ is influenced as little as possible by both the internal disturbances ($F_{\mathrm{d(pl)}}$) and the external disturbances ($F_{\mathrm{d(pl)}}$).
To suppress $F_{\mathrm{d(ext)}}$, a compliant suspension is required such that the payload and the floor are decoupled.
However, to enable suppression of the system disturbances $F_{\mathrm{d(pl)}}$, a stiff suspension is desirable to minimize the deflection of the payload~\citep{Voorhoeve2015SYSID}.
This obviously leads to a trade-off in the design.
In active vibration isolation, measurements of the position, velocity and even acceleration of the payload allow more freedom in tuning the suspension of the payload.
Typically, the controller $C$ acts as an additional damping term.
However, when such measurements are relative to the floor or other objects which are subject to the external disturbances $F_{\mathrm{d(ext)}}$ themselves, the trade-off for passive vibration isolation remains applicable.

On the other hand, when a measurement of the absolute velocity of the payload is available, the external disturbances can be reduced effectively.
Absolute velocity measurements can be obtained e.g. from inertial sensors~\citep{Collette2011} such as geophones~\citep{Rademakers2005MSc,Vandermaas2011MSc}.
In particular, such sensors suspend an inertial mass using suspension with very low resonance frequency to the payload.
By observing the relative movement of the inertial mass and the payload, the absolute velocity of the payload can be measured~\citep{Collette2011}.
Conceptually, the active controller $C$ can be seen as connected to an imaginary fixed point in the `sky' (\figref{fig:lrmhinf:vibration-isolation:skyhook}), which is not disturbed by $F_{\mathrm{d(ext)}}$ for an ideal sensor.
Consequently, the trade-off that exists in passive isolation is no longer relevant.
A compliant passive suspension can decouple the payload from external disturbances while the active controller acts as a stiff damper to the `sky' such that the effect $F_{\mathrm{d(pl)}}$ is suppressed.

The particular \gls{AVIS} used for the experiments, consists of a support fixed to the ground and a payload platform, suspended on airmounts (see \figref{fig:lrmhinf:avis:details}) providing passive vibration isolation.
The payload platform is able to move in six mechanical degrees of freedom.
Six geophones measure the payload velocity in an inertial reference frame, hence providing absolute velocity measurements, and eight linear motors (see \figref{fig:lrmhinf:avis:details}) allow to actively compensate for vibration of the platform using the principle of `sky-hook damping'.
Please refer to \appref{app:avis-setup} for more details regarding the mechanical set-up, placement of the sensor and the signal processing involved.
To facilitate the presentation, only the vertical translative velocity ($v_z$), i.e. a \gls{SISO} system, is considered.

@@

The parametrization of the plant model set $\ModelSet[]$ conforms to the dual-\YK{} framework~\citep{Hansen1989,Anderson1998} that parametrizes $\ModelSet[]$ in terms of  all plants $P$ that are stabilized by the controller $C$:
\begin{equation}
  \ModelSet[] 
    \isdef 
      \Set{
            \frac{\hat{N} + D_c \Delta}
                 {\hat{D} - N_c \Delta} 
          |
            \hinfnorm{\Delta} \leq \gamma
        }
  \label{eq:lrmhinf:dualYoulaModelSet}
  \text{,}
\end{equation}
where $C=N_c D_c^{-1}$ and $\estimated\Plant = \estimated{N}\estimated{D}^{-1}$ are decomposed as \gls{RCF} (see \figref{fig:lrmhinf:dualYoula}).
To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:lrmhinf:dualYoula} are required.
These can be computed from $u$ and $y$ directly~\citep{Anderson1998}.
%TODO{formules Hansen schema}
In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:lrmhinf:LPMHinf} applies.
